The evolution of badges of status with learners

### 2019-07-26 QD_report.Rmd
Various edits in report and graph, trying (unsuccesfully) to include results in the Arollo talk

>>>>

```{r loadData, echo=FALSE,include=FALSE}
# Required libraries -----------------------------------------------------------

library(here)
here()
source(here("AccFunc.R"))
# Scenario to be plotted - corresponds to folders where simulations are stored
scenario<-"mutType"
(listTest<-list.files(here("Simulations",paste0(scenario,"_"))))
(evolList<-grep(".txt",grep("evol",listTest,value=TRUE),value=TRUE))
(indList<-grep("ind",listTest,value=TRUE))

fileId<-1
evol<-fread(here("Simulations",paste0(scenario,"_"),evolList[fileId]))
pop<-fread(here("Simulations",paste0(scenario,"_"),indList[fileId]))
evolStats<-evol[,.(m.freqGenHawk=mean(freqGenHawks),
                   upIQR.freqGenHawk=fivenum(freqGenHawks)[4],
                   lowIQR.freqGenHawk=fivenum(freqGenHawks)[2],
                   m.freqGenDove=mean(freqGenDove),
                   upIQR.freqGenDove=fivenum(freqGenDove)[4],
                   lowIQR.freqGenDove=fivenum(freqGenDove)[2],
                   m.freqEval=mean(freqGenEval),
                   upIQR.freqGenEval=fivenum(freqGenEval)[4],
                   lowIQR.freqGenEval=fivenum(freqGenEval)[2], 
                   m.freqFenHawk=mean(freqFenHawks),
                   upIQR.freqFenHawk=fivenum(freqFenHawks)[4],
                   lowIQR.freqFenHawk=fivenum(freqFenHawks)[2],
                   m.freqFenDove=mean(freqFenDoves),
                   upIQR.freqFenDove=fivenum(freqFenDoves)[4],
                   lowIQR.freqFenDove=fivenum(freqFenDoves)[2],
                   m.meanAlpha=mean(meanAlpha),
                   upIQR.alpha=fivenum(meanAlpha)[4],
                   lowIQR.alpha=fivenum(meanAlpha)[2],
                   m.meanBeta=mean(meanBeta),
                   upIQR.beta=fivenum(meanBeta)[4],
                   lowIQR.beta=fivenum(meanBeta)[2],
                   m.freqHH = mean(freqHH),
                   m.freqHD = mean(freqHD),
                   m.freqDD = mean(freqDD),
                   upIQR.freqHH = fivenum(freqHH)[4],
                   upIQR.freqHD = fivenum(freqHD)[4],
                   upIQR.freqDD = fivenum(freqDD)[4],
                   lowIQR.freqHH = fivenum(freqHH)[4],
                   lowIQR.freqHD = fivenum(freqHD)[2],
                   lowIQR.freqDD = fivenum(freqDD)[2],
                   m.weightAct_0=mean(WeightAct_0),
                   m.weightAct_1=mean(WeightAct_1),
                   m.weightAct_2=mean(WeightAct_2),
                   m.weightAct_3=mean(WeightAct_3),
                   m.weightAct_4=mean(WeightAct_4),
                   m.weightCrit_0=mean(WeightCrit_0),
                   m.weightCrit_1=mean(WeightCrit_1),
                   m.weightCrit_2=mean(WeightCrit_2),
                   m.weightCrit_3=mean(WeightCrit_3),
                   m.weightCrit_4=mean(WeightCrit_4)),by=time]
# Extract means and IQR for the dynamic variables ------------------------------

popStats<-pop[, as.list(unlist(lapply(.SD, 
                                      function(x) list(m = mean(x),
                                                       upIQR = fivenum(x)[4],
                                                       downIQR = fivenum(x)[2]
                                      )))),
              by = time, 
              .SDcols=c("Quality","alpha","beta","Badge","nInteract","WeightAct_0",
                        "WeightAct_1","WeightAct_2","WeightAct_3","WeightAct_4",
                        "WeightCrit_0","WeightCrit_1","WeightCrit_2",
                        "WeightCrit_3","WeightCrit_4")]

# knitr::include_graphics("Simulations/mutType_/basicHawkDove.png")
```

### 2019-07-26 QD_report.tex
Various edits in report and graph, trying (unsuccesfully) to include results in the Arollo talk

\hypertarget{the-effect-of-learning}{%
\section{The effect of learning}\label{the-effect-of-learning}}

We let individuals have a \emph{badge of status} that potentially
signals their quality. To allow for this signalling, we let the size of
the \emph{badge of status} of an individual be dependent on her quality
through a reaction norm. we assume the size of the \emph{badge} is a
value from 0 to 1. This value is given by \begin{equation}
s_i = \frac{1}{1+e^{-(\alpha_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation} The parameters \(\alpha\) and \(\gamma\) in equation
\ref{eq:react_norm} determine the shape of the reaction norm, and hence,
how honest the \emph{badge} is in signalling the quality of the
individual.Eventually, the aim is to allow the signalling system to
evolve, by letting the parameters of the reaction norm be inherited from
parent to offspring and be change by a mutational process.

\hypertarget{how-does-learning-work}{%
\subsection{How does learning work?}\label{how-does-learning-work}}

@@

\hypertarget{results-when-individuals-do-not-vary-in-their-quality}{%
\subsection{Results when individuals do NOT vary in their
quality}\label{results-when-individuals-do-not-vary-in-their-quality}}

@@

\hypertarget{overall-effect-of-variance}{%
\subsection{Overall effect of
variance}\label{overall-effect-of-variance}}

@@

\hypertarget{how-does-learning-look-like-in-the-hawk-dove-game}{%
\subsection{How does learning look like in the Hawk-Dove
game?}\label{how-does-learning-look-like-in-the-hawk-dove-game}}

@@

\hypertarget{cited-literature}{%
\section*{Cited literature}\label{cited-literature}}
\addcontentsline{toc}{section}{Cited literature}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-sutton_reinforcement_2018}{}%
Sutton, Richard S., and Andrew G. Barto. 2018. \emph{Reinforcement
Learning: An Introduction}. Edited by Francis Bach. Second edition
edition. Cambridge, MA: A Bradford Book.

>>>>

\section{The effect of learning}\label{the-effect-of-learning}

We let individuals have a \emph{badge of status} that potentially
signals their quality. To allow for this signalling, we let the size of
the \emph{badge of status} of an individual be dependent on her quality
through a reaction norm. we assume the size of the \emph{badge} is a
value from 0 to 1. This value is given by

\begin{equation}
s_i = \frac{1}{1+e^{-(\alpha_i+\gamma_iQ_i)}}
\label{eq:react_norm}
\end{equation}

The parameters \(\alpha\) and \(\gamma\) in equation \ref{eq:react_norm}
determine the shape of the reaction norm, and hence, how honest the
\emph{badge} is in signalling the quality of the individual.Eventually,
the aim is to allow the signalling system to evolve, by letting the
parameters of the reaction norm be inherited from parent to offspring
and be change by a mutational process.

\subsection{How does learning work?}\label{how-does-learning-work}

@@

\subsection{Results when individuals do NOT vary in their
quality}\label{results-when-individuals-do-not-vary-in-their-quality}

@@

\subsection{Overall effect of
variance}\label{overall-effect-of-variance}

@@

\subsection{How does learning look like in the Hawk-Dove
game?}\label{how-does-learning-look-like-in-the-hawk-dove-game}

@@

\section*{Cited literature}\label{cited-literature}
\addcontentsline{toc}{section}{Cited literature}

\hypertarget{refs}{}
\hypertarget{ref-sutton_reinforcement_2018}{}
Sutton, Richard S., and Andrew G. Barto. 2018. \emph{Reinforcement
Learning: An Introduction}. Edited by Francis Bach. Second edition
edition. Cambridge, MA: A Bradford Book.
